\thesistitle

### 2019-07-28 sections/clonerefactor.tex
Better? Better.

Although the duplicate relations allow for variability in the equality arrays as long as it falls under the threshold, negative numbers in the equality array may never vary. This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored in the same way:
\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2)\text{ }x<0 \lor y<0 \Rightarrow x=y
\end{equation}

@@

Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance. The graph is traversed, starting from the last node in the code fragment (equal to graph traversal during clone detection). Because of that, $C_1$ $I_1$ is the very last clone instance in this example.

>>>>

In this graph, the duplicate relations (green arrows) do not necessarily denote an exact match. The duplicate relations allow for variability in the equality arrays as long as it falls under the variability threshold. However, negative numbers in the equality array may never vary. This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored as easily:
\begin{equation}\label{eq:t2rcloneequality}
E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2)\text{ }x<0 \lor y<0 \Rightarrow x=y
\end{equation}

@@

Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance. The process by which these clones are found is equal to the clone detection process as described in section \ref{sec:detectingclones}. In this example, we see the four clones found on the graph of figure \ref{fig:clonerefactorprocess}. Three of these clone classes have a two clone instances, each consisting of a single nodes. The other clone class has three clone instances, each consisting of two nodes.
